My title

### 2023-03-30 outputs/paper/paper.qmd
wrote up the danceability of flight of the bumblebees

4.  His response to the media

@@

I looked at the valence measures on Flight of the Bumblebee, a song that's much faster and "upbeat" than Mars and Jupiter. What I found complicated my understanding of valence -- different performance of the same song had different valence scores.

```{r}
# sub_planets<- read.csv(here::here("inputs/data/subset_planets.csv"))
# sub_planets |>
#   select(artist_name, valence, track_name) |>
#   head() |>
#   knitr::kable(
#     col.names = c("Artist Name", 
#                   "Valence", 
#                   "Track Name")
#  )

>>>>

4.  His tongue in cheek response to the media

@@

I looked at the valence measures on Flight of the Bumblebee, a song that's much faster and "upbeat" than Mars and Jupiter. What I found complicated my understanding of valence -- different performances of the same song had different valence scores. Some were arias, played by different instruments. These tend to have higher valence scores. The lowest recorded valence is 0.2410, and the highest is .9230. What gives?

```{r}
sub_bees<- read.csv(here::here("inputs/data/subset_bumblebee.csv"))
sub_bees |>
   select(artist_name, valence, album_release_year, track_name) |>
   head(17) |>
   knitr::kable(
     col.names = c("Artist Name", 
                   "Valence",
                   "Album Release Year",
                   "Track Name")
  )
